---
title: "[pm1] Visualization & Analysis"
author: "Egor Ananyev"
date: "2019-05-22"
output:
    html_document:
        toc: true
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Data input and parsing
```{r set-options, message=F}
options(width=100)
```

```{r}
shocky = F
# options(width=90)  # temp
library(plyr)
library(ggplot2)
if(shocky){ dropbox_dir='/Users/Egor/Dropbox' }else{ dropbox_dir='/Users/egora/Dropbox' }
data_dir = paste(dropbox_dir, 'Projects/pm/data/pm1/', sep='/')
subjs = dir(data_dir, pattern='subj-')
ds = data.frame()
# cur_subj = subjs  # temp
for(cur_subj in subjs){
  cur_subj_dir = paste0(data_dir, cur_subj)
  blocks = dir(cur_subj_dir, pattern='block-')
  # cur_block = blocks  # temp
  for(cur_block in blocks){
    cur_ds = read.csv(paste(paste(cur_subj_dir, cur_block, sep='/'), 'beh_out.csv', sep='/'))
    # ds = cur_ds  # temp
    ds = rbind(ds, cur_ds)
  }
}
rm(blocks, cur_block, cur_subj, cur_ds, cur_subj_dir, shocky)
# Useful columns
ds$loc_corr = as.numeric(as.character(ds$stim_loc) == as.character(ds$resp_loc))
ds$loc_corr_ = 'Correct'
ds$loc_corr_[ds$loc_corr==0] = 'Incorrect'
ds$loc_corr_ <- factor(ds$loc_corr_, c('Incorrect','Correct'))
loc_corr_lab = 'Location Response'
ds$soa_ = paste0('SOA=', ds$soa)
ds$resp_num_ = 'None'
ds$resp_num_[ds$resp_num==1] = 'One'
ds$resp_num_[ds$resp_num==2] = 'Two'
ds$resp_num_ <- factor(ds$resp_num_, c('None', 'One', 'Two'))
resp_num_lab = 'Reported Stimulus Number'
ds$angle_diff = 1
ds$angle_diff[ds$stim1_ori == ds$stim2_ori] = 0
ds$angle_diff_ = 'Same'
ds$angle_diff_[ds$angle_diff==1] = 'Different'
ds$angle_diff_ <- factor(ds$angle_diff_, c('Same','Different'))
ds$resp_ori_ = 'One'
ds$resp_ori_[ds$resp_ori=='B'] = 'Two'
resp_ori_lab = 'Reported Orientation Number'
ds$vis = 0
ds$vis[ds$resp_num>0] = 1
ds$vis_ = 'Invisible'
ds$vis_[ds$vis==1] = 'Visible'
vis_lab = ''
# Printing to screen
head(ds)
# 'Visible' trials only:
ds_vis = ds[ds$resp_num>0,]
```

# Visualization functions
```{r}
# A function for plotting y as a function of (afo) contrast of the two stimuli:
afo_contrast = function(df, fill_str, fill_lab){
  df[,'stim1_c'] = as.factor(df[,'stim1_c'])
  df[,'stim2_c'] = as.factor(df[,'stim2_c'])
  df[,fill_str] = as.factor(df[,fill_str])
  p = ggplot(data=df, aes_string(x='stim1_c', y='count', fill=fill_str)) + 
    facet_grid(reformulate('stim2_c', '.')) + geom_bar(stat='identity') + 
    labs(fill=fill_lab, x='Stimulus Contrasts (x = First Stimulus)', y='Trial Count') + 
    theme_bw() + theme(legend.position='top')
  print(p)
}
afo_contrast2 = function(df, fill_str, fill_lab){
  df[,'stim1_c'] = as.factor(df[,'stim1_c'])
  df[,'stim2_c'] = as.factor(df[,'stim2_c'])
  df[,fill_str] = as.factor(df[,fill_str])
  p = ggplot(data=df, aes_string(x='stim2_c', y='count', fill=fill_str)) + 
    facet_grid(reformulate('stim1_c', '.')) + geom_bar(stat='identity') + 
    labs(fill=fill_lab, x='Stimulus Contrasts (x = Second Stimulus)', y='Trial Count') + 
    theme_bw() + theme(legend.position='top')
  print(p)
}
# Count as a function of SOA:
afo_soa = function(df, fill_str, fill_lab){
  df[,'soa'] = as.factor(df[,'soa'])
  df[,fill_str] = as.factor(df[,fill_str])
  p = ggplot(data=df, aes_string(x='soa', y='count', fill=fill_str)) + 
    geom_bar(stat='identity') + labs(fill=fill_lab, x='Stimulus Onset Asynchrony',
                                     y='Trial Count') + 
    theme_bw() + theme(legend.position='top')
  print(p)
}
# Count as a function of angle difference:
afo_angle = function(df, fill_str, fill_lab){
  df[,'angle_diff_'] = as.factor(df[,'angle_diff_'])
  df[,fill_str] = as.factor(df[,fill_str])
  p = ggplot(data=df, aes_string(x='angle_diff_', y='count', fill=fill_str)) + 
    geom_bar(stat='identity') + labs(fill=fill_lab, x='Orientation',
                                     y='Trial Count') + 
    theme_bw() + theme(legend.position='top')
  print(p)
}
# Count as a function of SOA and angle difference:
afo_soa_angle = function(df, fill_str, fill_lab){
  df[,'soa'] = as.factor(df[,'soa'])
  df[,'angle_diff_'] = as.factor(df[,'angle_diff_'])
  df[,fill_str] = as.factor(df[,fill_str])
  p = ggplot(data=df, aes_string(x='soa', y='count', fill=fill_str)) + 
    facet_grid(reformulate('angle_diff_', '.')) + geom_bar(stat='identity') + 
    labs(fill=fill_lab, x='SOA x Orientation', y='Trial Count') + 
    theme_bw() + theme(legend.position='top')
  print(p)
}
afo_contrast_soa = function(df, fill_str, fill_lab){
  df[,'stim1_c'] = as.factor(df[,'stim1_c'])
  df[,'stim2_c'] = as.factor(df[,'stim2_c'])
  df[,'soa_'] = as.factor(df[,'soa_'])
  df[,fill_str] = as.factor(df[,fill_str])
  p = ggplot(data=df, aes_string(x='stim1_c', y='count', fill=fill_str)) + 
    facet_grid(reformulate('stim2_c', 'soa_')) + geom_bar(stat='identity') + 
    labs(fill=fill_lab, x='Stimulus Contrasts', y='Trial Count') + 
    theme_bw() + theme(legend.position='top')
  print(p)
}
afo_angle_soa = function(df, fill_str, fill_lab){
  df[,'soa_'] = as.factor(df[,'soa_'])
  df[,'angle_diff_'] = as.factor(df[,'angle_diff_'])
  df[,fill_str] = as.factor(df[,fill_str])
  p = ggplot(data=df, aes_string(x='angle_diff_', y='count', fill=fill_str)) + 
    facet_grid(reformulate('soa_', '.')) + geom_bar(stat='identity') + 
    labs(fill=fill_lab, x='Orientation', y='Trial Count') + 
    theme_bw() + theme(legend.position='top')
  print(p)
}
```

# Visibility

## Visibility ~ Contrast
```{r, fig.width=9.5, fig.height=2.5}
# print(colnames(ds))  # debug
ds_conf = ddply(ds, .(subj, vis_, stim1_c, stim2_c), summarise, 
                count=length(vis_))
afo_contrast(df=ds_conf, fill_str='vis_', fill_lab=vis_lab)
afo_contrast2(df=ds_conf, fill_str='vis_', fill_lab=vis_lab)
# ds_loc = ddply(ds, .(subj, loc_corr_, stim1_c, stim2_c), summarise, count=length(loc_corr_))
# afo_contrast(df=ds_loc, fill_str='loc_corr_', fill_lab=loc_corr_lab)
```

## Visibility ~ SOA
```{r, fig.width=3.5, fig.height=2.5}
ds_conf = ddply(ds, .(subj, vis_, soa), summarise, count=length(vis_))
afo_soa(df=ds_conf, fill_str='vis_', fill_lab=vis_lab)
# ds_loc = ddply(ds, .(subj, loc_corr_, soa), summarise, count=length(loc_corr_))
# afo_soa(df=ds_loc, fill_str='loc_corr_', fill_lab=loc_corr_lab)
```

## Visibility ~ Orientation Difference
```{r, fig.width=2.5, fig.height=2.5}
ds_conf = ddply(ds, .(subj, vis_, angle_diff_), summarise, count=length(vis_))
afo_angle(df=ds_conf, fill_str='vis_', fill_lab=vis_lab)
# ds_loc = ddply(ds, .(subj, loc_corr_, angle_diff_), summarise, count=length(loc_corr_))
# afo_angle(df=ds_loc, fill_str='loc_corr_', fill_lab=loc_corr_lab)
```

## Visibility ~ SOA x Orientation
```{r, fig.width=4.5, fig.height=2.5}
ds_conf = ddply(ds, .(subj, vis_, soa, angle_diff_), summarise, 
                count=length(vis_))
afo_soa_angle(df=ds_conf, fill_str='vis_', fill_lab=vis_lab)
# ds_loc = ddply(ds, .(subj, loc_corr_, soa, angle_diff_), summarise, count=length(loc_corr_))
# afo_soa_angle(df=ds_loc, fill_str='loc_corr_', fill_lab=loc_corr_lab)
```

## Visibility ~ Contrast x SOA
```{r, fig.width=9.5, fig.height=4.5}
# print(colnames(ds))  # debug
ds_conf = ddply(ds, .(subj, vis_, stim1_c, stim2_c, soa_), summarise, 
                count=length(vis_))
afo_contrast_soa(df=ds_conf, fill_str='vis_', fill_lab=vis_lab)
# ds_loc = ddply(ds, .(subj, loc_corr_, stim1_c, stim2_c, soa_), summarise, count=length(loc_corr_))
# afo_contrast_soa(df=ds_loc, fill_str='loc_corr_', fill_lab=loc_corr_lab)
```

# Number judgment

## Number ~ Orientation x SOA (visible)
```{r, fig.width=4.5, fig.height=2.5}
ds_num = ddply(ds_vis, .(subj, resp_num_, soa_, angle_diff_), summarise, 
               count=length(resp_num_))
afo_angle_soa(df=ds_num, fill_str='resp_num_', fill_lab=resp_num_lab)
```

## Number ~ Contrast x SOA
```{r, fig.width=9.5, fig.height=4.5}
ds_num = ddply(ds_vis, .(subj, resp_num_, stim1_c, stim2_c, soa_), summarise, 
               count=length(resp_num_))
afo_contrast_soa(df=ds_num, fill_str='resp_num_', fill_lab=resp_num_lab)
```

# Orientation judgment

## Orientation ~ Orientation x SOA (visible)
```{r, fig.width=6.5, fig.height=4.5}
ds_ori = ddply(ds_vis, .(subj, resp_ori, soa_, stim1_ori, stim2_ori), summarise, 
               count=length(resp_ori))
ds_ori$stim1_ori = paste('First =', ds_ori$stim1_ori)
ds_ori$stim2_ori = paste('Second =', ds_ori$stim2_ori)
afo_angles = function(df, fill_str, fill_lab){
  df[,'soa_'] = as.factor(df[,'soa_'])
  df[,'stim1_ori'] = as.factor(df[,'stim1_ori'])
  df[,'stim2_ori'] = as.factor(df[,'stim2_ori'])
  df[,fill_str] = as.factor(df[,fill_str])
  p = ggplot(data=df, aes_string(x='soa_', y='count', fill=fill_str)) + 
    facet_grid(reformulate('stim1_ori', 'stim2_ori')) + geom_bar(stat='identity') + 
    labs(fill=fill_lab, x='SOA x Stimulus Orientation', y='Trial Count') + 
    theme_bw() + theme(legend.position='top')
  print(p)
}
afo_angles(df=ds_ori, fill_str='resp_ori', fill_lab='Orientation Response')
```

## Orientation ~ SOA
```{r, fig.width=4.5, fig.height=2.5}
ds_ori = ddply(ds_vis, .(subj, resp_ori_, soa_, angle_diff_), summarise, 
               count=length(resp_num_))
afo_angle_soa(df=ds_ori, fill_str='resp_ori_', fill_lab=resp_ori_lab)
```

## Orientation ~ Contrast x SOA
```{r, fig.width=9.5, fig.height=4.5}
ds_ori = ddply(ds_vis, .(subj, resp_ori_, stim1_c, stim2_c, soa_), summarise, 
               count=length(resp_ori_))
afo_contrast_soa(df=ds_ori, fill_str='resp_ori_', fill_lab=resp_ori_lab)
```

# Number x Orientation judgment

## Same orientations presented
```{r, fig.width=9.5, fig.height=4.5}
ds_num = ddply(ds_vis[ds_vis$angle_diff==0,], .(subj, resp_num_, stim1_c, stim2_c, soa_), 
               summarise, count=length(resp_num_))
afo_contrast_soa(df=ds_num, fill_str='resp_num_', fill_lab=resp_num_lab)
```

## Different orientation presented
```{r, fig.width=9.5, fig.height=4.5}
ds_num = ddply(ds_vis[ds_vis$angle_diff==1,], .(subj, resp_num_, stim1_c, stim2_c, soa_), 
               summarise, count=length(resp_num_))
afo_contrast_soa(df=ds_num, fill_str='resp_num_', fill_lab=resp_num_lab)
```
